The Role of MPAs in Bycatch Reduction

### 2021-03-26 README.Rmd
passing to squid

>>>>

starginw thi hastings botsford weakstock species etc. can you hedge around this or not?Build intuition around BWMPAs for weakstocks

Covariance matrix across species: perfectly correlated to totally uncorrelated and everything in between

Clean up by setting Hastings and Botsford as a perfect template for this. PNAS? Isolate the life history

It is clear that if species are mutually exclusive, there is no potential for overlap protection... but where does it fall when overlap is something in between

Hmmm you could use virtual species.. or I guess that's even too complicated

What if you just picked an "environmental" variable, and generated a random matrix

For each species, you then assign a beta to that variable, where when they are all the same the covariance across the species is high. When they are all near zero there is no correlation, when they are opposite signs they are negatively correlated?

Suppose you had two variables actually. One specifies kind of the "default" distributino for all species. The other is an environmental variable, and species can have coefficients that on average range from all 1, evenly split 1 and -1, and near zero

Ah ok what about this. YOu define a set of benchmark species, where those benchmark species are defined by their relationship to a habitat. FOr the remainder of the species, their habitat is on average with noise on a gradient from -1 to 1, where one means they have the same as the benchmark, 0 means they are uncorrlated with the benchmark species, and -1 they are negatively correlated.

```{r}

library(marlin)
library(tidyverse)

theme_set(marlin::theme_marlin())

resolution <- 20 # resolution is in squared patches, so 20 implies a 20X20 system, i.e. 400 patches

seasons <- 1

years <- 50

tune_type <- "depletion"

steps <- years * seasons

# for now make up some habitat

base_hab <- expand_grid(x = 1:resolution, y = 1:resolution) %>%
  mutate(habitat =  .05 * x * y) %>% 
  mutate(habitat = as.numeric(scale(habitat)))

hab_scenes <- expand_grid(scene = c("friends", "enemies","frenemies"), species = fruit[1:10]) %>% 
  group_by(scene) %>% 
  nest()

generate_hab <- function(species, homogifier = 1,scene,base_hab,sigma_hab = 1, beta_hab = 1){

  sigma_hab = .2

  sigma_block <- 0.1

  homogifier <- 0

  species <- hab_scenes$data[[1]]

  block_a <- species$species[1:5]

  block_b <- species$species[6:10]

  block_a_betas <- rnorm(length(block_a),1,sigma_block)

  block_b_betas <- rnorm(length(block_b), homogifier, sigma_block)

  species$betas <- c(block_a_betas, block_b_betas)

  species$habitat <- vector(mode = "list", length = nrow(species))

  for (i in 1:nrow(species)){

    base_hab$realized_hab <- rnorm(nrow(base_hab), base_hab$habitat * species$betas[i], sigma_hab)

    species$habitat[[i]] <- base_hab

  }

  (species$habitat[[1]] %>% 
    ggplot(aes(x,y,fill = realized_hab))+ 
    geom_tile() + 
    scale_fill_viridis_c()) + 
      (species$habitat[[10]] %>% 
    ggplot(aes(x,y,fill = realized_hab))+ 
    geom_tile() + 
    scale_fill_viridis_c())

}

```

### 2021-03-26 documents/marlin-paper.Rmd
passing to squid

>>>>

what dooes the overlap tradeoff curve look like?

Suppose you close off 30% of an area in an MPA

Then plot conservation outcome on y-axis, degree of overlap between target and bycatch species on the x axis. When overlap is one, conservation benefit should be maxed. Then overlap is perfeclty anticorrelated, if effort concentrates, conservation should be at some negative minimum. If concentration doesn't happen, then conservation effect should be zero. If overlap is uncorrelated... unclear?

If there is perfect overlap, then improvement in coservation outcome should be a straight positive function of area protected. If there is no overlap, then
